X\texorpdfstring{\textsuperscript{2}}-Toon: An Extended X-Toon Shader

### 2013-04-15 paper/paper.tex

\begin{figure*}[h]
	\centering
	\includegraphics[width=5.5in]{images/hologram}
	\caption{Hologram result}
	\label{fig:hologram}
\end{figure*}

@@

\begin{figure*}[h]
	\centering
	\includegraphics[width=5.5in]{images/stipple-hatch-result1}
	\caption{Stipple/hatching result}
	\label{fig:stippleHatch1}
\end{figure*}

\begin{figure*}[h]
	\centering
	\includegraphics[width=5.5in]{images/stipple-hatch-result2}
	\caption{Stipple/hatching result}
	\label{fig:stippleHatch2}
\end{figure*}

\begin{figure*}[h]
  \centering
  \includegraphics[width=5.5in]{images/test}
  \caption{Sample illustration}
\end{figure*}

>>>>

\begin{figure*}[h]
	\centering
	\includegraphics[width=5.5in]{images/hologram}
	\caption{A hologram-like result. Textures from the model are not used, and a noise texture is used. As the y-axis on the 2D Texture decreases, the amount of noise increases.}
	\label{fig:hologram}
\end{figure*}

@@

\begin{figure*}[h]
	\centering
	\includegraphics[width=5.5in]{images/stipple-hatch-result1}
	\caption{A stipple and hatching-like result of an ant. A noise 2D texture was used. Vertices closer to the camera were more noisy, while those further away were transparent. The gaster of the ant looks like it was done through hatching, while the rest of its body looks like it was done through stipppling.}
	\label{fig:stippleHatch1}
\end{figure*}

\begin{figure*}[h]
	\centering
	\includegraphics[width=5.5in]{images/stipple-hatch-result2}
	\caption{A hatching-like result of an ant. A noise 2D texture was used. Vertices closer to the camera were more noisy, and looked more like hatches, while those further away were transparent.}
	\label{fig:stippleHatch2}
\end{figure*}

\begin{figure*}[h]
  \centering
  \includegraphics[width=5.5in]{images/test}
  \caption{Using a 2D texture from the original paper, we create a unique result by mixing the model's texture colors and the colors from the detail map.}
\end{figure*}
